CS6213 Project Report

### 2021-05-07 report/paper.tex
Small edits

@@

    \item We developed a prototype testing framework on top of \etcd to simulate execution traces generated by TLC against their actual Raft implementation, covering a representative subset of Raft's functionality.
    %
    This led to us discovering more specification omissions.

    \item We outlined a number of guidelines which we believe are applicable to any implementation of the same approach.

    \item We believe model-based test case generation is a promising approach, with its main deterrent being the amount of effort required to carefully model every detail of a mature implementation. Still, it does not require specialised knowledge and does provide the link between model and implementation we hoped for.

@@

The idea is to feed a trace into the implementation and check if the implementation also arrives at the final state. Used this way, a trace serves as a test case.
%
To do that, the implementation must be extended with

@@

    \item An interpreter for actions. In some sense this may be seen as a concretization function, mapping a specification action to an implementation state change.
\end{enumerate}

@@

We chose \etcd \footnote{\url{https://etcd.io/}}, a distributed key-value store, for our experiments.
%
It is notable for being the most widely-used Raft implementation in production \footnote{\url{https://github.com/etcd-io/etcd/blob/master/raft/README.md}}, implementing many of the extensions described in Ongaro's thesis \cite{ongaro_consensus_2014}. It also has a comprehensive test suite utilising fault injection \footnote{\url{https://github.com/etcd-io/etcd/blob/master/tests/functional/README.md}}.
%
This made it ideal for testing our hypotheses that 1. widely-used implementations could have deep protocol bugs that 2. fault injection would not be able to find.

@@

We did not find any bugs in the implementation, only specification omissions, and arguably rather specific to \etcd's behaviour.

@@

We believe that our model-based test case generation approach is promising as it allows us to link specification to implementation, taking advantage of the redundancy to identify discrepancies \cite{fonseca2017empirical}.
%
The changes to the implementation are not invasive, e.g.~it is not required that it be reimplemented in a different language, merely that the interpreter is additionally implemented.

>>>>

    \item We started developing a prototype testing framework on top of \etcd to simulate execution traces generated by TLC.

@@

@@

The idea is to feed a trace into the implementation and check if the implementation also arrives at the ``same'' final state. Used this way, a trace serves as a test case.
%
To do that, the implementation must be extended with

@@

    \item An interpreter for actions. This may be seen as a concretization function, mapping a specification action to an implementation state change.
\end{enumerate}

@@

We chose \etcd\footnote{\url{https://etcd.io/}}, a distributed key-value store, for our experiments.
%
It is notable for being the most widely-used Raft implementation in production\footnote{\url{https://github.com/etcd-io/etcd/blob/master/raft/README.md}}, implementing many of the extensions described in Ongaro's thesis \cite{ongaro_consensus_2014}, including multiple-at-a-time membership changes with joint consensus as well as PreVote and CheckQuorum~\cite{howard_raft_2020}.
%
It also has a comprehensive test suite utilising fault injection\footnote{\url{https://github.com/etcd-io/etcd/blob/master/tests/functional/README.md}}.
%
This made it ideal for testing our hypotheses that (1) widely-used implementations could have deep protocol bugs which (2) fault injection would not be able to find.

@@

We did not find any bugs in the implementation, only specification omissions.

@@

We believe that our model-based testing approach is promising as it allows us to link specification to implementation, taking advantage of the redundancy to identify discrepancies \cite{fonseca2017empirical}.
%
The changes to the implementation are not invasive, e.g.~it is not required that it be reimplemented in a different language, merely that the interpreter is additionally implemented.
